Extended Data

### 2021-04-27 doc/manuscript/Dow_Extended_Data.Rmd
added chronology counts

tree_rings_TMIN_short_caption <- "Extended Data Figure 3 | Sensitivity of annual growth, as derived from tree-rings, to monthly minimum temperatures, for ## chronologies from ## sites across eastern North America. Chronologies are grouped by xylem porosity and ordered by mean April T_max. Chronology details are given in the Supplementary Information. (**NOTE: Figure still needs some work. Chronology numbers are off.**  See [GitHub Issue #49](https://github.com/EcoClimLab/growth_phenology/issues/49).)"

>>>>

tree_rings_TMIN_short_caption <- "Extended Data Figure 3 | Sensitivity of annual growth, as derived from tree-rings, to monthly minimum temperatures, for 207 chronologies from 114 sites across eastern North America. Chronologies are grouped by xylem porosity and ordered by mean April T_max. Chronology details are given in the Supplementary Information. (**NOTE: Figure still needs some work. Chronology numbers are off.**  See [GitHub Issue #49](https://github.com/EcoClimLab/growth_phenology/issues/49).)"

### 2021-04-27 doc/manuscript/Dow_manuscript_Nature.Rmd
added chronology counts

tree_rings_caption <- "Figure 4 | Sensitivity of annual growth, as derived from tree-rings, to monthly maximum temperatures, for ## chronologies from ## sites across eastern North America. Chronologies are grouped by xylem porosity and ordered by mean April T_max. Chronology details are given in the Supplementary Information. (NOTE: Figure still needs some work. **COLOR SCALE IS  A BIT OFF.**  See [GitHub Issue #49](https://github.com/EcoClimLab/growth_phenology/issues/49).)"

@@

###~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## some stats/ 
species_table <- read.csv(file = "tables_figures/species_table.csv")
n_dendro_trees <- sum(na.omit(species_table[, "n.trees"]))
n_tree_years <- sum(na.omit(species_table[, "n.tree.years"]))
n_cores_focal_sites <- sum(na.omit(species_table[, "n.cores"]))
n_chronologies <- NA
n_cores_sites <- NA
n_chronologies_SCBI <- NA
n_chronologies_HF <- NA
```

@@

# Supporting Information

>>>>

tree_rings_caption <- "Figure 4 | Sensitivity of annual growth, as derived from tree-rings, to monthly maximum temperatures, for 207 chronologies from 114 sites across eastern North America. Chronologies are grouped by xylem porosity and ordered by mean April T_max. Chronology details are given in the Supplementary Information. (NOTE: Figure still needs some work. **COLOR SCALE IS  A BIT OFF.**  See [GitHub Issue #49](https://github.com/EcoClimLab/growth_phenology/issues/49).)"

@@

###~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## some stats/ 
species_table <- read.csv(file = "tables_figures/species_table.csv")
n_dendro_trees <- sum(na.omit(species_table[, "n.trees"]))
n_tree_years <- sum(na.omit(species_table[, "n.tree.years"]))
n_cores_focal_sites <- sum(na.omit(species_table[, "n.cores"]))
chronology_table <- read.csv(file = "tables_figures/chronology_table.csv")
n_chronologies <- nrow(chronology_table)  #!!! entered by hand in figure captions
n_cores_sites <- length(unique(chronology_table[, "Location"])) #!!! entered by hand in figure captions
n_chronologies_SCBI <- 12
n_chronologies_HF <- 3
```

@@

# Additional Information

**Supplementary Information** is available for this paper.

Correspondence and requests for materials should be addressed to Kristina Anderson-Teixeira (teixeirak@si.edu).
